Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Slides are finished

>>>>

\begin{frame}{Conclusions}
We proposed a new test statistic for the null hypothesis that the data follow a Gamma distribution, i.e., they are fully developed speckle or come from textureless areas.
Noteworthy points:
\begin{itemize}[<+->]
	\item The test statistic estimates the Shannon entropy non-parametrically,
	\item It has excellent size (small Type~I error) and power (small Type~II error),
	\item It produces a map of $p$ values,
	\item It correctly identifies trees as not homogeneous, but also not extremely heterogeneous, differently from  tests based on the coefficient of variation.
\end{itemize}
\end{frame}
